MSE Scenarios for short and long lived

### 2025-04-15 Scenarios.Rmd
update for long lived (redfish-like)

# Selectivity Configuration
fleet_pars <- c(5,1)
index_pars <- c(2,1)
sel <- list(model=rep("logistic",n_fleets+n_indices),
            initial_pars=c(rep(list(fleet_pars),n_fleets),rep(list(index_pars),n_indices)))

# M Configuration
M <- list(model="constant",initial_means=array(0.1, dim = c(n_stocks,n_regions,n_ages)))

@@

# Set para. for B-H function
alpha <- 12
beta  <- 1.5e-4

@@

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 3,
               recruit_pars = rep(list(c(alpha,beta)),n_stocks), # assume same B-H s-r functions for all stocks
               sigma_vals = sigma_vals,
               N1_pars = N1_pars)#,
               #NAA_where = basic_info$NAA_where)

>>>>

# Selectivity Configuration
# for logistic pars are a50 and 1/slope
# approximate from redfish model
fleet_pars <- c(9,1)
index_pars <- list(c(5,1), c(3,1))
sel <- list(model=rep("logistic",n_fleets+n_indices),
            initial_pars=c(rep(list(fleet_pars),n_fleets),
                           #rep(list(index_pars),n_indices)))
                           index_pars))

# redfish M is 0.05 but I'll leave this at 0.1 
# M Configuration
M <- list(model="constant",initial_means=array(0.1, dim = c(n_stocks,n_regions,n_ages)))

@@

# # Set para. for B-H function, not using
# alpha <- 12
# beta  <- 1.5e-4

@@

NAA_re <- list(N1_model=rep(ini.opt,n_stocks),
               sigma=rep(sigma,n_stocks),
               cor=rep(re_cor,n_stocks),
               recruit_model = 2,
               #recruit_pars = rep(list(c(alpha,beta)),n_stocks), # assume same B-H s-r functions for all stocks
               sigma_vals = sigma_vals,
               N1_pars = N1_pars)#,
               #NAA_where = basic_info$NAA_where)
